Excel Constraints

### 2016-03-08 Notes/Description.tex
Work in progress on algorithm

>>>>

\section{Constraint-view Algorithm}
\subsection{Input}
The input to the algorithm consists of a set of version spaces~$S$ describing a hierarchical set of vectors.

Additionally the user specifies if he wants the most general, specific or all solutions.
This bias is captured is captured in the refinement operator~$\rho_2$ which traverses version spaces based on the bias.

Implicitly this algorithm also uses a catalogue of constraints~$C$, an oracle~$O$ to calculate constraints and background knowledg~$B$ about 1) constraints and 2) properties.

\subsection{Output}
This algorithm~$\rho_1$ returns a set of constraints where the variables are instantiated by (sub-)version spaces contained in~$S$.

\subsection{Method}
In this case we will assume that a constraint~$c \in C$ has be selected to be learned.

\begin{itemize}
 	\item For every free variable~$x$ in~$c$, prune~$S$ to obtain candidate values~$S_x$ using the properties that have been calculated so far: repeat:
 	\item For every version space~$s$ in~$S_x$, choose~$s$ as a value for $x$ and proceed
 	\item Use~$\rho_2$ to return the 
 \end{itemize}
